---
title: "201 Population Growth Modeling"
author: "Elmera Azadpour"
date: "1/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

### Going off of "Logistic Population Growth and Harvesting" handout on GS
```{r}
# a function for dN/dt
calc_dNdt <- function(r, N, K) {r*N*(1-N/K)}  

# some values for r and K (constants)
r <- 0.5
K <- 100

# make some dummy data for population sizes
N <- 0:100

# calculate a dN/dt for each value of N
dNdt <- calc_dNdt(r=r, N=N, K=K)

# plot the result
plot(N, dNdt, type = "l", xlab="Population Size, N",ylab="rate of change, dN/dt",
xaxs="i", yaxs='i',xlim=c(0,110),ylim=c(0,15))
```

At low population size, dNdt is small (because there are not many
individuals making more individuals) but rapidly increasing as N increases. The population reaches some maximum growth rate somewhere in the middle, and then again reaches zero at N = K. Why does dNdt = 0 at N = K? Think about the equation for logistic growth above. Let’s label this point.